---
title: "Assignment 2: Visualization by example"
author: FirstName LastName
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(palmerpenguins))
```

## Exercise 1

i. 344 Rows and 8 total columns

ii. It is an observation of penguin and their features

iii. Species, Island, and Sex

iv. bill length in mm, bill depth in mm, flipper length in mm, and body mass in g

v. Year

vi. Gentoo, Chinstrap, and Adelie


## Exercise 2

```{r}
 qplot(x = flipper_length_mm, data = penguins)
```

i. x-axis

ii. The number of penguins with a flipper length

iii. The graph is bimodal with 2 or 3 peaks, more information is required to give a definite mode


## Exercise 3

i.
```{r}
 qplot(x = flipper_length_mm, data = penguins, bins=15)
```

ii.
```{r}
 qplot(x = flipper_length_mm,binwidth=1, data = penguins)
```

## Exercise 4

```{r}
qplot(x = flipper_length_mm, y = body_mass_g, data = penguins)
```

i. Body mass

ii. There is a non-linear positive relationship in the scatter plot

## Exercise 5

```{r}
qplot(x = bill_length_mm, y = body_mass_g, data = penguins)
```
The correlation in this scatter plot looks weaker then the plot of the last


## Exercise 6

```{r}
qplot(x = bill_length_mm, y = body_mass_g, data = penguins, geom = c("point", "smooth"), method = "lm")
```
I feel that this graph is communicated batter without the trend line because there is less data points the further up you go on the x-axis. The data is much more gather towards the center of the graph so the trend line follows the outliers to much in this case.

## Exercise 7

```{r}
qplot(x = bill_length_mm, y = body_mass_g, data = penguins, geom = c("point", "smooth"), color = species, method = "lm")
```
Adding color helps focus the previously very scattered graph. Now that each species has their own trend line it helps contextualize the previous outliers and groupings into making more sence.

